\documentclass[10pt]{resume}
\usepackage[left=0.4in,top=0.2in,right=0.4in,bottom=0.2in]{geometry}
\usepackage{hyperref}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}



\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{HARSHIT GYANCHANDANI}

\address{ \href{tel:+919321745632}{+91 9321745632} \\
Mumbai, Maharashtra \\ \href{mailto:harshitgyanchandani@gmail.com}{harshitgyanchandani@gmail.com} \\
 \href{https://github.com/Harshit332004}{Github} \\
 \href{https://www.linkedin.com/in/harshit-gyanchandani-5292a9294/}{Linkedin}}


\begin{document}

%----------------------------------------------------------------------------------------
%\tPROFESSIONAL SUMMARY
%----------------------------------------------------------------------------------------

\begin{rSection}{Professional Summary}
Aspiring software engineer specializing in Flutter app development with a strong foundation in full-stack technologies (Node.js, Firebase, MongoDB). Experienced in building scalable, production-ready mobile apps with clean architecture. Comfortable working across both cross-platform and native Android (Jetpack Compose) stacks. Passionate about building impactful, user-friendly apps through efficient, modern mobile development.

\end{rSection}

%----------------------------------------------------------------------------------------
%\tEDUCATION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
\textbf{University of MUMBAI– Thadomal Shahani Engineering College} \hfill \textit{Expected May 2026} \\
Bachelor of Engineering in Information Technology \hfill Mumbai, India \\
\textit{Relevant Coursework:} Data Structures, Algorithms, Database Management Systems, Web/App Development, Software Engineering, Operating Systems
\end{rSection}


%----------------------------------------------------------------------------------------
%\tSKILLS
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}
\textbf{Languages:} Python • Dart • C • Kotlin • Java \quad
\textbf{Frameworks/Tools:} Flutter SDK • Jetpack Compose • Node.js • REST API • Firebase • Git \quad
\textbf{Databases:} MongoDB • MySQL • SQLite (Room)
\end{rSection}

%----------------------------------------------------------------------------------------
%\tPROJECTS
%----------------------------------------------------------------------------------------
\begin{rSection}{Projects}

\textbf{Cryptozz} — Jetpack Compose (Android), REST API, Firebase 
\href{https://github.com/Harshit332004/CryptocurrencyApp-Retrofit}{\underline{[GitHub]}} \\
\textit{Cryptocurrency Tracker App} \\
• Implemented real-time crypto tracking using Jetpack Compose. \\
• Integrated REST APIs for live price data and Firebase Firestore for storing user preferences. \\
• Built on MVVM architecture with LiveData and coroutines for auto-refresh every 5 minutes. 

\textbf{Expense Tracker (Major Project)} — Flutter, Node.js, MongoDB, Firebase Auth 
\href{https://github.com/Harshit332004/Expense_Tracker}{\underline{[GitHub]}} \\
\textit{Income and Expense Management App} \\
• Developed a cross-platform app with receipt image logging. \\
• Integrated Node.js backend and Firebase Auth for secure login. \\
• Used MongoDB for structured financial data storage. \\
• Built a conversational AI interface for navigation, adding transactions, and querying financial data. 

\textbf{ValoScans (Ongoing)} — Flutter, REST API, Firebase Auth \\
\textit{Valorant Player Stats Visualizer} \\
• Building a dashboard for match analytics, win/loss trends, and real-time MMR estimates using Riot API. \\
• Implemented hybrid data-fetching using official APIs and web scrapers for unsupported endpoints. 

\end{rSection}


%----------------------------------------------------------------------------------------
%\tEXPERIENCE
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}
\vspace{-0.75em}

\item \textbf{Mobile App Development Apprentice} — Project Recycle-it \\
• Developed and integrated core features of a Flutter-based recycling app using Provider for state management. \\
• Implemented user authentication, waste category selection, and pickup request submission with Firebase Firestore as the backend. \\
• Collaborated under mentorship to improve app performance and maintain clean, modular architecture. \\
• App adopted by local government with 120+ active users, streamlining waste management processes.

\end{rSection}


%----------------------------------------------------------------------------------------
%\tCERTIFICATIONS
%----------------------------------------------------------------------------------------

\begin{rSection}{Certifications}
\vspace{-0.5em}
• Mastering Android App Development with Kotlin (XML + Compose) – Coursera \href{https://www.udemy.com/certificate/UC-070146a7-cdbf-4be6-b49b-6bd2ab065a74/}{[View]} \\
• Flutter Course for Beginners – FreeCodeCamp (via Class Central)
\end{rSection}

%----------------------------------------------------------------------------------------
%\tEXTRACURRICULAR
%----------------------------------------------------------------------------------------

\begin{rSection}{Extra-Curricular Activities}
\vspace{-0.5em}
• Member of technical committee \textbf{CodeTantra}, contributed to event planning and tech outreach. \\
• Volunteered with \textbf{Clean Malad Initiative}. Designed and deployed Project Recycle-it, a mobile app with 120+ users promoting sustainability and environmental awareness.
\end{rSection}

\end{document}
